\LARGE \bf Robust Task Wrench Resistance \vspace{-2ex} \versionline{0}

### 2016-08-04 ICRA2017/paper.tex
Added wrench resistance paper

\begin{document}
\title{\LARGE \bf Dex-Net 1.0: A Cloud-Based Network of 3D Objects for Robust Grasp Planning Using a Multi-Armed Bandit Model with Correlated Rewards
	\vspace{-2ex}
	\versionline{14}}
\author{Jeffrey Mahler$^1$, Florian T. Pokorny$^1$, Brian Hou$^1$, Melrose Roderick$^1$, Michael Laskey$^1$, Mathieu Aubry$^{1,2}$, \\
Kai Kohlhoff$^3$, Torsten Kroeger$^3$, James Kuffner$^3$, Ken Goldberg$^{1}$
%\vspace{-2ex}
\thanks{{\small $^1$ University of California, Berkeley, USA; {\tt\small \{jmahler, ftpokorny, brian.hou, goldberg\}@berkeley.edu, melrose\_roderick@brown.edu}}}%
%\thanks{$^2$IEOR Dept; {\tt\small goldberg@berkeley.edu}}%
%\thanks{$^{1-2}$ University of California, Berkeley, USA}%
\thanks{{\small $^2$ Universit\'e Paris-Est, LIGM (UMR CNRS 8049), ENPC, France. {\tt\small mathieu.aubry@enpc.fc}}}%
\thanks{{\small $^3$ Google Inc., Mountain View, USA; {\tt\small \{kohlhoff, tkr, kuffner\}@google.com}} }
}
\maketitle

%\TODO{Possibly will include Matthieu Aubry, Alyosha Efros, and Pieter Abbeel as coauthors} \\
%\TODO{Update number of models in title: I want it to reflect exactly how many we use in experiments}
%\TODO{Trim paper to 8 pages}
\input{includes/abstract}
%
\input{includes/introduction}
\input{includes/related_work}
%
\input{includes/problem_statement}
\input{includes/dataset}
%\input{includes/background}
\input{includes/algorithm}
\input{includes/experiments}
\input{includes/conclusion}

%%\appendix
%\include{includes/proofs}

\section{Acknowledgments}
{\small
This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS)``People and Robots" Initiative: http://robotics.citris-uc.org.
The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, by grants from Google, Cisco, and UC Berkeley's Algorithms, Machines, and People Lab; and by the Department of Defense (DoD) through the National Defense Science \& Engineering Graduate Fellowship (NDSEG) Program.
We thank our colleagues who wrote code for the project, in particular Raul Puri, Sahaana Suri, Nikhil Sharma, and Josh Price, as well as our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Alyosha Efros, Animesh Garg, Kevin Jameison, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, Nan Tian, and Jur van den Berg.
}

>>>>

\begin{document}
\title{\LARGE \bf Robust Task Wrench Resistance
	\vspace{-2ex}
	\versionline{0}}
\author{Jeffrey Mahler$^1$, Jacky Liang$^1$, Ken Goldberg$^1$
%\vspace{-2ex}
\thanks{{\small $^1$ University of California, Berkeley, USA; {\tt\small \{jmahler, jackyliang, goldberg\}@berkeley.edu}}}% }
}
\maketitle

\input{includes/abstract}

\input{includes/introduction}

\input{includes/related_work}

\section{Acknowledgments}
{\footnotesize
This research was performed in UC Berkeley's Automation Sciences Lab under the UC Berkeley Center for Information Technology in the Interest of Society (CITRIS) ``People and Robots" Initiative: http://robotics.citris-uc.org.
The authors were supported in part by the U.S. National Science Foundation under NRI Award IIS-1227536, by grants from Google, UC Berkeley's Algorithms, Machines, and People Lab; the Knut and Alice Wallenberg Foundation; the NSF-Graduate Research Fellowship; and the Department of Defense (DoD) through the National Defense Science \& Engineering Graduate Fellowship (NDSEG) Program.
We thank our colleagues who gave feedback and suggestions, in particular Pieter Abbeel, Animesh Garg, Kevin Jamieson, Sanjay Krishnan, Sergey Levine, Zoe McCarthy, Stephen McKinley, Sachin Patil, and Nan Tian.
}
